\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}

\hypersetup{breaklinks=true,%
pagecolor=white,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}

\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}


\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Header     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resume_header}
\name{Adam Gaddis}
\program{ Data Science Major -- Business Analytics Major}
\contact{agaddis02@live.com \hspace{2cm} (214) 335 - 3200 \hspace{2cm}2015 E Overton Rd}
\end{resume_header}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%     About Me     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resume_section}{About Me}
  \begin{nospacetabbing}

  \textbf{Programming Languages}  \= C\#, Python, Java, LabVIEW, R, SQL, MQL5, JS, HTML, CSS, LaTeX\\*
  \textbf{BI Tools} \> Tableau, Spotfire, Power BI\\*
  \textbf{Office Certifications} \> Excel, Access, Word, PowerPoint\\*
  \textbf{Interests} \> Big Data, Robotics, AI Automation, Car Detail\\*
  \end{nospacetabbing}

\end{resume_section}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Geek Squad     %
%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{resume_section}{Work Experience}
  \begin{resume_employer}{Geek Squad}{Consultation Agent}{Dallas, TX}{November 2019 - Present}
    \item Diagnose and understand customers problems quickly
    \item Troubleshoot technology on site
    \item translate problems into words for ARA's effectively
  \end{resume_employer}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Scout     %
%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{resume_employer}{Scout Energy Partners}{Accounting Intern}{Dallas, TX}{Summer 2019}
    \item Contribute any design ideas/thoughts on main Spotfire workbook
    \item Scan/File completed JIB(Joint Interest Billing) entries. 
    \item Help in the process of creating and finishing JIB entries and JIB details for various properties and 
    interest holders using P2 and excel.
    \item Utilize P2 Excalibur for the entry of AFE’s.
    \item Utilize excel in conjunction with P2 for multiple auto calculated fields within immensely fleshed out 
   excel workbooks.
   \item Use of IRON Python for better and more in-depth statistical analysis of data.
  \end{resume_employer}
\end{resume_section}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Richland     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resume_section}{Education}
  \begin{resume_subsection}[Dallas, TX (2016--2020)]{Richland College}
    \begin{subitems}
    \item Associates of Applied Science Software Programmer/Developer
     \item GPA: 3.61
      \item CIT - Programmer (Level I) 05/19
      \item Local Dallas County Community College District partnered with Emmett J. Conrad’s Global Collegiate Academy. Awards students with 60 college credit hours, and an Associate’s Degree in Applied Science
    \end{subitems}
  \end{resume_subsection}
  
%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Conrad     %
%%%%%%%%%%%%%%%%%%%%%%%%%%
  
  \begin{resume_subsection}[Dallas, TX (2016--2020)]{Emmett J. Conrad Global Collegiate Academy}
    \begin{subitems}
     \item GPA: 3.67
      \item Early College Academy focused on the progression of STEAM in Texas. First graduating class of the newly founded program.

     \end{subitems}
  \end{resume_subsection}
\end{resume_section}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%     FRC     %
%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{resume_section}{Competitions and Personal Projects}
  \begin{resume_subsection}[(August 2016 - Present)]{FIRST Robotics | FRC Team 3005 RoboChargers}
  \begin{subitems}
    \item Lead Data Scientist - Constructed data visualizations used to compare competition data for strategical planning prior to matches. Assisted the Scouting and Drive Team decide on alliance partners for elimination matches. 
    \item Lead Student Strategist – Read and analyze visualized data for alliance selections in preparation for eliminations. Analyze each year’s challenge to understand what a “star” robot will look like. 
    \end{subitems}
  \end{resume_subsection}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Trading Bot     %
%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{resume_subsection}[(Present)]{FOREX GBPUSD Automated Trading Bot}
  \begin{subitems}
    \item In current delevopment of a automated trading bot for the currency exchange between the Great British Pound and the US Dollar
    \item Using MQL5 and machine learning packages to study the flow of each currency and pinpoints peak positions to enter trades
    \item auto sets Buy Stops, Stop Losses, and automatically commences trades and ends trades
    \item Set to make a 5x income inrease on any starting cash amount \$500 or more
    \end{subitems}
  \end{resume_subsection}


\end{resume_section}
\end{document}